3D MAGNETIC MODELLING FOR ELLIPSOIDS

### 2016-09-27 manuscript/Paper-magnetic-elipsoid_metodologia.tex
paper-elipsoid introducao e metodologia do elipsoide

%% 2-Column Papers and Discussion Papers
\documentclass[journal abbreviation, manuscript]{copernicus}

@@

\introduction  %% \introduction[modified heading if necessary]
TEXT

\section{Methodology}
TEXT

\subsection{Triaxial Ellipsoid}
The implementation of the forward problem of a triaxial ellipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its center is the center of this ellipsoidal body.

We will define this new coordinate system ($x_1,x_2,x_3$) by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect to the geographic axis $x$, $y$ e $z$:
\loadeq{043}
\loadeq{044}\
\loadeq{045} 
\\

The angles refering to the unit vectors are determined by the orientations of the ellipsoid's semi-axis. The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180º. Meanwhile $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane. Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the ellipsoid's center with the geographic plane.

Thus, the coordinates of the body's semi-axis are given by:
\loadeq{046}

@@

For an ellipsoid of semi-axis $a > b > c$, the equation that defines yours surface is:
\loadeq{030}

@@

There is, however, a set of values for $s (\lambda,\mu,\nu)$, which are roots of the cubic equation:
\loadeq{031}

This set of roots, called ellipsoidal coordinates, correspond to parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates. Their expressions are:
\loadeq{038}\
\loadeq{039}\
\loadeq{040}

Where:
\loadeq{032}\
\loadeq{033}\
\loadeq{034}\
\loadeq{035}\
\loadeq{036}\
\loadeq{037}\

The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:elipsoide}, where $s$ admits the value of $\lambda$.
\loadeq{010}

@@

The desmagnetization factors are given by:
\loadeq{047}
\loadeq{048}
\loadeq{049}

Where $F(\theta,k)$ e $E(\theta,k)$ are first and second Legendre's normal elliptical integrals, respectively. To calculate $k$ and $\theta$ we have the following expressions:
\begin{equation}
k = \sqrt{\left(\dfrac{a^2-b^2}{a^2-c^2} \right)}
\end{equation}

@@

The susceptibility tensor matrix is:
\loadeq{050}

The Earth's field vector, $F$, and the remanent magnetization ,$d$, also must be converted to the body's coordinates:
\loadeq{051}
\loadeq{052}

@@

In the case that the body has a very low susceptibility ($\chi < 0.1$ SI) the self-demagnatization is negligible and the resultant magnetic vector is given by:
\loadeq{053}

For values bigger than 0.1 SI the resultant magnetic vector is:
\loadeq{055}

Where:
\loadeq{054}

@@

\loadeq{056}
\loadeq{057}
\loadeq{058}

where:
\loadeq{059}\\
\loadeq{060}\\
\loadeq{061}\\
\loadeq{062}\\

And:
\loadeq{063}\\

Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's elliptical integrals. While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an ellpsoid. This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:
\begin{equation}
U_i(x_1,x_2,x_3) = \pi abc G \rho \int_{0}^{\infty} \left[1 - \dfrac{x_1^2}{a^2+u} - \dfrac{x_2^2}{b^2+u} - \dfrac{x_3^2}{c^2+u}\right] \dfrac{du}{R(u)}
\end{equation}

@@

Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient and will help us better see the inverse problem ahead. Thus, the magnetic field generated by the ellipsoid is:
\loadeq{007}

With:
\loadeq{009}\\
\loadeq{011}\\

For $j = 1,...,L$, the number of ellipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:
\loadeq{006}

We must remember that every calculation so far was done using the body's coordinates, however the notation in equation \eqref{eq:campoGeo} the magnetic field is already in geographics coordinates. To calculate each component of the magnetic field's vector back:
\loadeq{064}
\loadeq{065}
\loadeq{066}

Been $\Delta T^0$, $i = 1,...,N$, the total field anomaly observed in positions (xi, yi, zi), mathematically it can be rewritten as:
\loadeq{001}

The total field vector $T_i$ can be represented by:
\loadeq{002}

Where $F_i$ is the magnetic field's vector and $B_i$ the magnetic induction's vector generated by the magnetic sources.
Considering $F_i$ a constant vector $F_0$ for local ou regional scale, and that $||F_0|| \gg ||B_0||$, since, $B_i$ is a small pertubation of the magnetic field $F_i$, we can approximate the euclidian norm of the vector $T_i$ by a Taylor's expansion of first order:
\loadeq{003}

where $T$ indicates transposition and
\loadeq{004}

is a unit vector that represents the gradient of the function $||T_i||$ in relation to the vector's components $T_i$. This way, we can approximate the equation \eqref{eq:anomalia} of total-field anomaly to:
\loadeq{005}

Substituting the magnetic induction' equation \eqref{eq:campoGeo} in the total magnetic induction \eqref{eq:campoGeoNL} and using the total-field anomaly approximation \eqref{Anomaliaaproximada} we obtain the predict anomaly for the total field produced by the $L$ ellipsoids:
\loadeq{018}

The equation \eqref{eq:anomaliaCompleta} can be rewritten as:
\loadeq{019}

Where:
\loadeq{020}

And:
\loadeq{021}

The equation \eqref{eq:anomaliaJ} shows the dependence for the predicted total-field anomaly related to the vector $h$. We can rewrite it in matrix notation:
\loadeq{022}

Been $A$ the matrix:
\loadeq{023}

With $a_i$, $i= 1,...,N$ the vector of dimension $3L$ defined in equation \eqref{eq:matrizsensibilidade}.

@@

\begin{thebibliography}{}

\bibitem[AUTHOR(YEAR)]{LABEL}
REFERENCE 1

\bibitem[AUTHOR(YEAR)]{LABEL}
REFERENCE 2

\end{thebibliography}

>>>>

%% 2-Column Papers and Discussion Papers
\documentclass[gmd, manuscript]{copernicus}

@@

\introduction  %% \introduction[modified heading if necessary]

The magnetic method is considered one of the oldest geophysics techniques. The greek philosofer Thales supposedly did the first obsevations on magnetism in the sixth century. The chineses in the XII century, already used magnetic compasses as an instrument for marine orientation \citep{nabighian2005historical}. During the World War II there was a need for instruments of several magnitudes of precision higher than was available at the time for detection of submarines by aeromagntic exploration. Thus, the fluxgate magnetometer was invented, expanding the use of this method for geophysic exploration \citep{reford1964aeromagnetics,hanna1924some}. The diffusion of this method was quick and well accepted whereas the possiblity  of covering large areas in a relativey short time \citep{blakely1996potential,nabighian2005historical}.

The applications of magnetic exploration includes several important study situations as estimating the average of basement relief, mapping geologic structures like faults and lithologic contacts; and also for mineral exploration, identifying mineral deposits and mapping geologic traps for oil and gas  \citep{oliveira2015estimation}.

In the decade of 1970 \cite{farrar1979some} showed in his work the value of the ellipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies of Tennant Crees's gold mine in Australia. The ellipsoid demonstrated to be the most competent geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.

In his book \textit{A Treatise on Electricity and Magnetism}, \cite{maxwell1881treatise} demonstrated that only shapes bounded by second degree surfaces are uniformly magnetized when placed in a uniform field. In the particular case of the ellipsoidal geometry, the intern magnetic field is independent of spatial coordinates, therefore its magnetization is completely homogeneous, making it the only geometric shape that has a true anlitic solution for self-desmagnetization \citep{clark1986magnetic}.

The magnetic field resultant of an ellipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes. Through a consistent notation this work tapped a hole in the literature that missed the ellipsoidal model. This model, however, consists in a division between prolate and oblate ellipsoids, with some differences in the algorithm.

In this work, we will implement a generalized model for triaxial ellipsoids published by \cite{clark1986magnetic}. From the solution of gravitational potential for uniform ellipsoids, formally solved by \cite{dirichlet1839nouvelle} in his article \textit{Sur un nouvelle methode pour la determination des integrales multiples}, that uses first and second Legendre's normal elliptic integrals, and using the Poisson's relation \citep{grant1965interpretation} it is possible to calculate the magnetic potential, and posteriorly the magnetic field generated by the body calculating the gradient of this potential.

\section{Methodology}
The total-field anomaly can be described as a difference between the total field vector and the induced magnetization of the crust of the Earth, thats includes any anomalous distribuition of magnetization that can occur by magnetizied bodies in subsurface. This difference can be written as:
\begin{equation} \label{eq:1}
\Delta T^0_i = ||T_i|| - ||F_i||,
\end{equation}
where $\Delta T^0_i$ is the observed vector of total-field anomaly in the $i$-th position ($x_i$, $y_i$, $z_i$), $i = 1,...N$, $F_i$ is the geomagnetic field and $||.||$ is the Euclidian norm. The total-field vector $T_i$ is:
\begin{equation}\label{eq:2}
T_i = F_i + B_i,
\end{equation}
and $B_i$ is the total induced magnetization vector produced by all sources of anomalous susceptibility distribuition.
Considering $F_i$ a constant vector, $F_0$ for local ou regional scale, and that $||F_0|| \gg ||B_0||$, since, $B_i$ is a small pertubation of the magnetic field $F_i$, we can approximate the euclidian norm of the vector $T_i$ by a Taylor's expansion of first order:
\begin{equation}\label{eq:3}
||T_i|| \approx ||F_0 + B_i|| \approx ||F_0|| + F^T B_i
\end{equation}
where $T$ indicates transposition and
\begin{equation}\label{eq:4}
\hat{F} = \dfrac{F_o}{||F_0||}
\end{equation}

is a unit vector that represents the gradient of the function $||T_i||$ in relation to the vector's components $T_i$. This way, we can approximate the Eq.(\ref{eq:1}) of total-field anomaly to:
\begin{equation}\label{eq:5}
\Delta T \approx \hat{F^T} B_i, \quad i=1,...,N
\end{equation}

\subsection{The Forward model of a sphere}

\subsection{The Forward model of a triaxial elipsoid}
The implementation of the forward problem of a triaxial ellipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its center is the center of this ellipsoidal body.

We will define this new coordinate system ($x_1,x_2,x_3$) by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect to the geographic axis $x$, $y$ e $z$:
\begin{equation}
\hat{v_1} = (l_1,m_1,n_1) = (-\cos\alpha \cos\delta, -\sin\alpha \cos\delta, -\sin\delta)
\end{equation}

\begin{equation}
\begin{split}
\hat{v_2} = (l_2,m_2,n_2) = (\cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma,\\ \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\gamma \cos\delta)
\end{split}
\end{equation}

\begin{equation}
\begin{split}
\hat{v_3} = (l_3,m_3,n_3) = (\sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta,\\ -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta, \sin\gamma \cos\delta)
\end{split}
\end{equation}

The angles refering to the unit vectors are determined by the orientations of the elipsoid's semi-axis. The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180$^{\circ}$. Meanwhile $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane. Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the ellipsoid's center with the geographic plane.

Thus, the coordinates of the body's semi-axis are given by:

\begin{equation}
x_h = (x-xc)l_h + (y-yc)m_h + (z-zc)n_h \quad (h= 1,2,3)
\end{equation}

@@

For an ellipsoid of semi-axis $a > b > c$, the equation that defines yours surface is:

\begin{equation} \label{eq:elipsoide}
\dfrac{x_1^2}{(a^2+s)} + \dfrac{x_2^2}{(b^2+s)} + \dfrac{x_3^2}{(c^2+s)} = 1
\end{equation}

@@

There is, however, a set of values for $s (\lambda,\mu,\nu)$, which are roots of the cubic equation:

\begin{equation} \label{eq:cubica}
s^3 + p_2s^2 + p_1s + p_0 = 0
\end{equation}

This set of roots, called ellipsoidal coordinates, correspond to parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates. Their expressions are:

\begin{equation}
\lambda = 2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} \right) - \dfrac{p_2}{3}
\end{equation}

\begin{equation}
\mu = -2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} + \dfrac{\pi}{3} \right) - \dfrac{p_2}{3}
\end{equation}

\begin{equation}
\mu = -2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} - \dfrac{\pi}{3} \right) - \dfrac{p_2}{3}
\end{equation}

Where:

\begin{equation}
p_0 = a^2b^2c^2 - b^2c^2x_1^2 - c^2a^2x_2^2 - a^2b^2x_3^2
\end{equation}

\begin{equation}
p_1 = a^2b^2 + b^2c^2 + c^2a^2 - (b^2+c^2)x_1^2 - (c^2+a^2)x_2^2 - (a^2+b^2)x_3^2
\end{equation}

\begin{equation}
p_2 = a^2 + b^2 + c^2 - x_1^2 - x_2^2 - x_3^2
\end{equation}

\begin{equation}
p = p_1 - \dfrac{p_2^2}{3}
\end{equation}

\begin{equation}
q = p_0 - \dfrac{p_1p_2}{3} + 2 \left(\dfrac{p_2}{3} \right)^3
\end{equation}

\begin{equation}
\theta = \cos^{-1} \left[\dfrac{-q}{2} \sqrt{\left(\dfrac{-p}{3} \right)^3} \right]
\end{equation}

The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:elipsoide}, where $s$ admits the value of $\lambda$.

\begin{equation}
\dfrac{\partial \lambda}{\partial x_1} = \dfrac{2x_1/(a^2+\lambda)}{\left(\dfrac{x_1}{a^2+\lambda}\right)^2 + \left(\dfrac{x_2}{b^2+\lambda}\right)^2 + \left(\dfrac{x_3}{c^2+\lambda}\right)^2}
\end{equation}

@@

The desmagnetization factors are given by:

\begin{equation}
N_1 = \dfrac{4 \pi abc}{(a^2-b^2)\sqrt{(a^2-c^2)}} [F(\theta,k) - E(\theta,k)]
\end{equation}

\begin{equation}
N_2 = \dfrac{4 \pi abc \sqrt{(a^2-c^2)}}{(a^2-b^2)(b^2-c^2)} \left[E(\theta,k) - \left(\dfrac{b^2-c^2}{a^2-c^2} \right) F(\theta,k) - \dfrac{c(a^2-b^2)}{ab \sqrt{(a^2-c^2)}} \right]
\end{equation}

\begin{equation}
N_3 = \dfrac{4 \pi abc}{(b^2-c^2)\sqrt{(a^2-c^2)}} \left[\dfrac{b \sqrt{(a^2-c^2)}}{ac} - E(\theta,k) \right]
\end{equation}

Where $F(\theta,k)$ e $E(\theta,k)$ are first and second Legendre's normal elliptical integrals, respectively. To calculate $k$ and $\theta$ we have the following expressions:

\begin{equation}
k = \sqrt{\left(\dfrac{a^2-b^2}{a^2-c^2} \right)}
\end{equation}

@@

The susceptibility tensor matrix is:

\begin{equation}
k_{ij} = \sum_r k_r (L_r l_i + M_r m_i + N_r n_i) (L_r l_j + M_r m_j + N_r n_j) \quad (r = 1,2,3)
\end{equation}

The Earth's field vector, $F$, and the remanent magnetization ,$d$, also must be converted to the body's coordinates:

\begin{equation}
F_h = F(l \, l_h + m \, m_h + n \, n_h)
\end{equation}

\begin{equation}
(J_N)_h = J_N (l_N l_h + m_n m_h + n_N n_h)
\end{equation}

@@

In the case that the body has a very low susceptibility ($\chi < 0.1$ SI) the self-demagnatization is negligible and the resultant magnetic vector is given by:

\begin{equation}
\tilde{J}_R = K\tilde{F} + \tilde{J}_{NRM}
\end{equation}

For values bigger than 0.1 SI the resultant magnetic vector is:

\begin{equation}
\tilde{J}_{Rc} = A^{-1} \tilde{J}_R
\end{equation}

Where:

\begin{equation}
A = I + KN = \left[\begin{matrix} 
1+k_{11}N_1 \quad & k_{12}N_2 \quad & k_{13}N_3 \\\\
k_{21}N_1 \quad & 1+k_{22}N_2 \quad & k_{23}N_3 \\\\
k_{31}N_1 \quad & k_{23}N_2 \quad & 1+k_{33}N_3
\end{matrix}\right]
\end{equation}

@@

\begin{equation} \label{eq:campo_e}
\Delta B_1 = f_1 \dfrac{\partial \lambda}{\partial x_1} - 2 \pi abc \, J_1 \, A(\lambda) 
\end{equation}

\begin{equation}
\Delta B_2 = f_1 \dfrac{\partial \lambda}{\partial x_2} - 2 \pi abc \, J_2 \, B(\lambda)
\end{equation}

\begin{equation}
\Delta B_3 = f_1 \dfrac{\partial \lambda}{\partial x_3} - 2 \pi abc \, J_3 \, C(\lambda)
\end{equation}

where:

\begin{equation}
f_1 = \dfrac{2\pi abc}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}} \left[\dfrac{J_1x_1}{a^2+\lambda} + \dfrac{J_2x_2}{b^2+\lambda} + \dfrac{J_3x_3}{c^2+\lambda}\right]
\end{equation}

\begin{equation}
A(\lambda) = \dfrac{2}{(a^2-b^2) \sqrt{(a^2-c^2)}} [F(\theta^{'},k) - E(\theta^{'},k)]
\end{equation}

\begin{equation}
B(\lambda) = \dfrac{2 \sqrt{(a^2-c^2)}}{(a^2-b^2)(b^2-c^2)} \left[ E(\theta^{'},k) - \left(\dfrac{b^2-c^2}{a^2-c^2} \right) F(\theta^{'},k) - \dfrac{k^2\sin\theta^{'}\cos\theta^{'}}{\sqrt{(1-k^2\sin^2\theta^{'})}} \right]
\end{equation}

\begin{equation} \label{eq:integralC}
C(\lambda) = \dfrac{2}{(b^2-c^2) \sqrt{(a^2-c^2)}} \left[\dfrac{\sin\theta^{'} \sqrt{(1-k^2\sin^2\theta^{'})}} {\cos\theta^{'}} - E(\theta^{'},k) \right]
\end{equation}

And:

\begin{equation}
\theta^{'} = \sin^{-1} \left(\dfrac{a^2-c^2}{a^2+\lambda}\right)^{0.5} \quad (0 \le \theta^{'} \le \pi/2) 
\end{equation}

Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's elliptical integrals. While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an ellpsoid. This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:

\begin{equation}
U_i(x_1,x_2,x_3) = \pi abc G \rho \int_{0}^{\infty} \left[1 - \dfrac{x_1^2}{a^2+u} - \dfrac{x_2^2}{b^2+u} - \dfrac{x_3^2}{c^2+u}\right] \dfrac{du}{R(u)}
\end{equation}

@@

Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient and will help us better see the inverse problem ahead. Thus, the magnetic field generated by the ellipsoid is:

\begin{equation}\label{eq:campoGeo}
b_i^j = 2\pi a_j b_j c_j \times [M_i^j - D_i^j] \times J^j \quad j=1,...,L
\end{equation}

With:

\begin{equation}
M_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
\left[\begin{matrix} 
\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{c^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{c^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{c^2+\lambda}
\end{matrix}\right]_{3 \times 3}
\end{equation}

\begin{equation}
D_i^j =
\left[\begin{matrix} 
A(\lambda) & 0 & 0 \\
0 & B(\lambda) & 0 \\
0 & 0 & C(\lambda)
\end{matrix}\right]
\end{equation}

For $j = 1,...,L$, the number of ellipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:

\begin{equation}\label{eq:campoGeoNL}
B_i = \sum_{j=1}^{L} b_i^j, \quad i=1,...,N
\end{equation}

We must remember that every calculation so far was done using the body's coordinates, however the notation in equation \eqref{eq:campoGeo} the magnetic field is already in geographics coordinates. To calculate each component of the magnetic field's vector back:

\begin{equation}
\Delta B_x = \Delta B_1l_1 + \Delta B_2l_2 + \Delta B_3l_3
\end{equation}

\begin{equation}
\Delta B_y = \Delta B_1m_1 + \Delta B_2m_2 + \Delta B_3m_3
\end{equation}

\begin{equation}
\Delta B_z = \Delta B_1n_1 + \Delta B_2n_2 + \Delta B_3n_3
\end{equation}

@@

%%\begin{thebibliography}{}

%%\bibitem[AUTHOR(YEAR)]{LABEL}
%%REFERENCE 1

%%\bibitem[AUTHOR(YEAR)]{LABEL}
%%REFERENCE 2

%%\end{thebibliography}

\bibliographystyle{copernicus}
\bibliography{references}
